Quantum-assisted unsupervised data clustering

### 2020-05-03 manuscript.tex
Fix this allows for a simple encoding #15

We now introduce an optimized algorithm for calculating the matrix of Hamming distances \cite{trugenberger2001} between a sample vector and all cluster vectors, making use of quantum parallelism.

%This allows for a simple encoding of the classical information into a quantum register.

>>>>

Using a known technique of encoding classical information into a quantum register, 
based on probabilistic quantum memories \cite{trugenberger2001},
we introduce an optimized algorithm for calculating the matrix of Hamming distances between each pair of binary vectors  of two sets taking advantage of quantum parallelism.
This allows for a simple encoding of the classical information into a quantum register.
